---
title: "p8105_hw5_cj2793"
author: "Chenyu Jin"
date: "2024-11-02"
output: github_document
---

```{r message = FALSE}
library(tidyverse)
set.seed(1)
```

# Problem 2

## Set design parameters according to the problem

```{r}
n <- 30
sigma <- 5
mu_values <- c(0:6)
iterations <- 5000
alpha <- 0.05
```

## Function to simulate data

```{r}
simulate_t_test <- function(mu, sigma = 5, n = 30) {
  x <- rnorm(n, mean = mu, sd = sigma)
  t_test_result <- t.test(x, mu = 0)
  tibble(
    estimate = t_test_result[["estimate"]],
    p_value = t_test_result[["p.value"]]
  )
}
```

## Run simulation for each value of mu

```{r}
simulation_results <- expand_grid(mu = mu_values, 
                                  iter = 1:iterations) |>
  mutate(
    result_df = map(mu, simulate_t_test)
  ) |>
  unnest(result_df)
```

## Calculate power for each mu value

```{r}
power_results <- simulation_results |>
  group_by(mu) |>
  summarize(power = mean(p_value < alpha))
```

## Plot power vs. true value of mu

```{r plot1}
power_results |>
  ggplot(aes(x = mu, y = power)) +
  geom_line() +
  geom_point() +
  labs(
    title = "Power of the One-Sample t-Test",
    x = "True Value of μ",
    y = "Power (Proportion of Null Rejected)"
  ) +
  theme_minimal()
```

The graph shows the relationship between the true value of μ and the power of the one-sample t-test. As the true value of μ increases, the power of the test also increases, indicating a higher probability of rejecting the null hypothesis when the effect size is larger.

## Average estimate of mu across all samples and only when null is rejected

```{r}
estimate_results <- simulation_results |>
  group_by(mu) |>
  summarize(
    avg_estimate_all = mean(estimate),
    avg_estimate_rejected = mean(estimate[p_value < alpha])
  )
```

## Plot average estimate vs. true value of mu

```{r plot2}
estimate_results |>
  ggplot(aes(x = mu)) +
  geom_line(aes(y = avg_estimate_all, color = "All Samples")) +
  geom_line(aes(y = avg_estimate_rejected, color = "Null Rejected")) +
  geom_point(aes(y = avg_estimate_all, color = "All Samples")) +
  geom_point(aes(y = avg_estimate_rejected, color = "Null Rejected")) +
  labs(
    title = "Average Estimate of μ vs. True Value of μ",
    x = "True Value of μ",
    y = "Average Estimate of μ",
    color = "Condition"
  ) +
  theme_minimal()

```

The graph shows the average estimate of μ across all samples and only for samples where the null hypothesis was rejected. The average estimate of μ for rejected tests tends to be higher than the true value, especially for smaller effect sizes, because only larger estimates pass the significance value alpha = 0.05.